A Rapid Feasibility Checking for Reconfiguration of Mismatched PV Arrays

### 2019-06-01 PVSC-46/Manuscript/PVSC_Manuscript.tex
modified by Prof. Ooshita

%In final version, please replace the following two definitions
\newcommand{\michiko}{\textcolor{blue}}
%\newcommand{\michiko}{\textcolor{black}}

@@

\section{Introduction}\label{Sec1}
As fossil fuel depletion and environmental pollution become more serious, green and renewable energy has become necessary for a sustainable society and environment. 
Photovoltaic (PV) systems receive significant attention since the sun has unlimited energy and PV arrays can be easily scaled up. 
However, due to the nature of PV cell, which is a basic component of a PV array, PV arrays are sensitive to partial shading and PV cell damage. 
PV cells could not uniformly generate power when they experience different irradiances or some of them have physical defects, and such a mismatched condition might accelerate heating and aging of PV cells and cause further damaging. 
To prevent PV cells from damaging, bypass diodes are usually placed in PV arrays and they are turned on in mismatched conditions. 
However,  the operation of bypass diode will cause a number of PV cells to stop deliver power, %
\michiko{and it will hence result in a significant loss of power generation. }

% it will introduce voltage drop which cause PV panel mismatched.
% However, it causes a significant loss of power generation.

PV arrays are hierarchically constructed such that a group of PV cells form a PV module, a group of PV modules form a PV panel, and a group of PV panels form a PV array. 
Power generation of mismatched PV arrays can be recovered by reconfiguring connection of these components. 
Fig.\ref{compare} shows an example of power generations of a PV array with a partial shading. 
We distributed shading cells non-uniformly to a PV array with 3 $\times$  4 PV panels and applied power simulation. 
Before reconfiguration, \michiko{there are} multiple \michiko{peaks in a power - voltage curve with similar power levels,} while, after we reconfigured connection among PV panels, 
\michiko{some peaks exhibit much higher power levels than others and }
%MPPs has reduced and 
power generation increased by 35\%.

@@

For the method in \cite{orozco2016optimized}, first, close values \michiko{of extracted currents or voltages are} approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
Then possible combinations of reconfiguration are enumerated.
For each candidate configuration \michiko{its generated} power value \michiko{is} estimated by \cite{orozco2015fast} along with careful estimation of possible errors.
For example, Table \ref{tab:monitored} shows extracted currents for 4 panels each of which has 3 modules, and they are approximated into four current levels as shown in Table \ref{tab:approximated}. 
% Then currents and voltages of MPPs are approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
As mentioned in Section \ref{Sec2}, if some panel has $m$ MPPs with current level of $I$ or larger, $m$ modules can be active with current level of $I$. 
Table \ref{tab:modules} shows the maximum number of active modules for each current level.
Control voltage for one PV model is approximated to 20V.
Approximated power values for possible configurations are shown in Table \ref{tab:powers}. 
% Then power values are approximated for possible configurations. 
Table \ref{tab:powers} shows an example to form a PV array with two strings,
%where power value is simply multiplied PV array current with control voltage .
\michiko{where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V), and power values of strings are obtained as products of current and voltage values. For example, when current levels of two strings are 3A and 2.5A and the number of active modules per string is 3, the control voltage is 60V, and two strings generate powers of $3\mbox{A} \times 60\mbox{V} = 180\mbox{W}$ and $2.5\mbox{A} \times 60\mbox{A} = 150\mbox{W}$, and the total generated power is 330W.}

@@

Step 3 optimizes the number of active modules. 
In Step 3, if the number of active modules exceeds the required number $m$, redundant panels are canceled if exist. 
A panel is \textit{redundant} if the number of active modules is still $m$ or more even if the panel is canceled.  
Redundant panels are searched \michiko{for each loss level}. 
Starting with a loss level where the last panel is selected, we check the number of active modules $M_{p}(Q_{n})$ for each panel $p$ 
where $Q_{n}$ is a required current level for the current string.
Redundant panels are selected and canceled from panels with less number of $M_{p}(Q_{n})$ in the same loss level. 
If \michiko{the number of active modules} still exceeds $m$ after canceling,
the same procedure is applied to the previous loss level.
% we will go to the previous loss level and try to cancel panels.
This procedure is repeated until selecting an exactly $m$ active modules or checking all the loss levels.
\michiko{This step accurately finds redundant panels if exist in the following reason. Since the number of active modules in one panel is 0, 1, 2, or 3 and panels are selected from panels with less active modules in the same loss level, if the number of active modules exceed $m$, the surplus is 1 or 2. That means, the last selected panel has 2 or 3 active modules, and panels with 1 or 2 active modules have already selected if exist.}

@@

\michiko{To evaluate the proposed method, we prepared MPP informations of 100 mismatched PV arrays and applied our algorithm. We also applied an exhaustive searching algorithm for comparison.
MPP information is setup as follows for each PV array. 
Each PV array has 6 - 24  panels and the number of PV panels is randomly determined. 
Three current values are randomly assigned to the three modules in each panel from 3 - 8 current values, where the number of possible current values are also randomly determined for each PV array. 
The number of strings after reconfiguration is 3 - 6 and it is randomly determined for each PV array.}

>>>>

%In final version, please replace the following two definitions
\newcommand{\michiko}{\textcolor{blue}}
%\newcommand{\michiko}{\textcolor{black}}
\newcommand{\zhao}{\textcolor{red}}

@@

\section{Introduction}\label{Sec1}
As fossil fuel depletion and environmental pollution become more serious, green and renewable energy has become necessary for a sustainable society and environment. 
Photovoltaic (PV) systems receive significant attention since the sun has unlimited energy and PV arrays can be easily scaled up. 
However, due to the nature of PV cell, which is a basic component of a PV array, PV arrays are sensitive to partial shading and PV cell damage. 
PV cells could not uniformly generate power when they experience different irradiances or some of them have physical defects, and such a mismatched condition might accelerate heating and % power generation increased by 35\%.
\zhao{maximum output power increased by 35\%}.

@@

For the method in \cite{orozco2016optimized}, first, close values \michiko{of extracted currents or voltages are} approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
Then possible combinations of reconfiguration are enumerated.
For each candidate configuration \michiko{its generated} power value \michiko{is} estimated by \cite{orozco2015fast} along with careful estimation of possible errors.
For example, Table \ref{tab:monitored} shows extracted currents for 4 panels each of which has 3 modules, and they are approximated into four current levels as shown in Table \ref{tab:approximated}. 
% Then currents and voltages of MPPs are approximated and grouped into a small number of classes so that the number of possible combinations, or a search space, is reduced.
As mentioned in Section \ref{Sec2}, if some panel has $m$ MPPs with current level of $I$ or larger, $m$ modules can be active with current level of $I$. 
Table \ref{tab:modules} shows the maximum number of active modules for each current level.
Control voltage for one PV model is approximated to 20V.
Approximated power values for possible configurations are shown in Table \ref{tab:powers}. 
% Then power values are approximated for possible configurations. 
Table \ref{tab:powers} shows an example to form a PV array with two strings,
%where power value is simply multiplied PV array current with control voltage .
\michiko{where control voltages are approximated as multiples of 20V (the number of active modules per string times 20V), and power values of strings are obtained as products of current and voltage values. For example, when current levels of two strings are 3A and 2.5A and the number of active modules per string \zhao{are} 3, the control voltage is 60V, and two strings generate powers of $3\mbox{A} \times 60\mbox{V} = 180\mbox{W}$ and $2.5\mbox{A} \times 60\mbox{A} = 150\mbox{W}$, and the total generated power is \zhao{approximated about} 330W.}

@@

Step 3 optimizes the number of active modules. 
In Step 3, if the number of active modules exceeds the required number $m$, redundant panels \zhao{will be} canceled if exist. 
A panel is \textit{redundant} if the number of active modules is still $m$ or more even if \zhao{this} panel is canceled.  
Redundant panels are searched \michiko{for each loss level}. 
Starting with a loss level where the last panel is selected, we check the number of active modules $M_{p}(Q_{n})$ for each panel $p$ 
where $Q_{n}$ is a required current level for the current string.
Redundant panels are selected and canceled from panels with less number of $M_{p}(Q_{n})$ in the same loss level. 
If \michiko{the number of active modules} still exceeds $m$ after canceling,
the same procedure is applied to the previous loss level.
% we will go to the previous loss level and try to cancel panels.
This procedure is repeated until selecting an exactly $m$ active modules or checking all the loss levels.
\michiko{This step accurately finds redundant panels if exist in the following reason. Since the number of active modules in one panel is 0, 1, 2, or 3 \zhao{as assumed in Section \ref{Sec2}} and panels are selected from panels with less active modules in the same loss level, if the number of active modules exceed $m$, the surplus is 1 or 2. That means, the last selected panel has 2 or 3 active modules, and panels with 1 or 2 active modules have already selected if exist.}

@@

\michiko{To evaluate the proposed method, we prepared MPP informations of 100 mismatched PV arrays and applied our algorithm. We also applied an exhaustive searching algorithm for comparison.
MPP information is setup as follows for each PV array. 
Each PV array has 6 - 24  panels and the number of PV panels is randomly determined. 
Three current values are randomly assigned to the three modules in each panel from 3 - 8 current values, where the number of possible current values are also randomly determined for each PV array.
\zhao{\large \textbf{Is that means: Current value for PV modules in each PV panel are randomly assigned from 3 - 8 current values.}}
The number of strings after reconfiguration is 3 - 6 and it is randomly determined for each PV array.}
